LAGOS lake depth

### 2020-02-18 figures/00_maps.Rmd
embiggen legend points, closes #30

```{r 00_map_bathy, echo=FALSE, message=FALSE, eval=TRUE, warning=FALSE, results='hide', fig.width=6}
cowplot::plot_grid(gg_bathy, 
                   gg_shapeclass, 
                   ncol = 1)
```

>>>>

```{r 00_map_bathy, echo=FALSE, message=FALSE, eval=TRUE, warning=FALSE, results='hide', fig.width=6}
cowplot::plot_grid(gg_bathy + 
                     guides(
                       color = guide_legend(
                         override.aes = list(size = 2))), 
                   gg_shapeclass + 
                     guides(
                       color = guide_legend(
                         override.aes = list(size = 2))), 
                   ncol = 1)
```
